%-------------------------
% Resume in Latex
% Author : Aryan Sukhadan Nair
% Based on: https://github.com/AyushSNair/AutoCV
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Aryan Sukhadan Nair} \\ \vspace{1pt}
    Full Stack Developer \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ (+91) 9321442430 ~ \href{mailto:nairaryan135@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  nairaryan135@gmail.com} ~ 
    \href{https://linkedin.com/in/aryan-nair}{\raisebox{-0.2\height}\faLinkedin\ linkedin.com/in/aryan-nair}  ~
    \href{https://github.com/aryannair}{\raisebox{-0.2\height}\faGithub\ github.com/aryannair}
    \vspace{-8pt}
\end{center}
  
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fr. C. Rodrigues Institute of Technology}{Vashi, Maharashtra}
      {Bachelor of Engineering in Computer Engineering}{2022 -- 2026}
      \resumeItemListStart
        \resumeItem{CGPA: 9.20/10.0} (till SEM 6)
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IISER x Suraj Informatics}{Remote}
      {Project Intern}{Jul 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Working on YOLOv11-based smart vision system for real-time baggage counting}
        \resumeItem{Integrating ByteTrack, zone-based logic, and anomaly detection with live dashboard}
        \resumeItem{Enhancing accuracy and scalability for deployment in crowded environments}
      \resumeItemListEnd

    \resumeSubheading
      {Sports Mentoring Infusion - NGO}{Remote}
      {Full Stack Developer}{Jun 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Designed and implemented backend services using Node.js and PostgreSQL for Swabhav360, a platform aimed at supporting 100+ orphan students.}
        \resumeItem{Managed APK builds and handled overall integration between backend, frontend, and database.}
        \resumeItem{Built key features for student task module and admin module, including class management, coach/student assignments, daily task reviews, and    task allocation.}
        \resumeItem{Collaborated with the frontend team to enhance UI/UX for student and admin interfaces using React Native.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Society of India (CSI) FCRIT}{Vashi, Maharashtra}
      {Technical Head}{Jul 2024}
      \resumeItemListStart
        \resumeItem{Deployed and hosted the pre-built CSI website on the college domain, ensuring accessibility for all users.}
        \resumeItem{Updated website content to meet team requirements, including team section, past events, and current events displays.}
        \resumeItem{Contributed to the hackathon website by developing the domain page with detailed information about problem statements.}
      \resumeItemListEnd

    \resumeSubheading
      {IISER Mohali}{Mohali, Punjab}
      {Project Intern}{Jul 2024 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Preprocessed and analyzed 4 cardiovascular datasets; trained and compared Linear Regression, Logistic Regression, Random Forest, XGBoost, and SVM models on raw and processed data (1300+ pateint data).}
        \resumeItem{Integrated Gemini API for medical report uploads and AI-powered explanations using Gemini 2.5.}
        \resumeItem{Built healthcare web app with CVD risk prediction (Framingham Risk Score + ML models), interactive health history graphs, and secure file/profile management.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Swabhav360 -- Impact Tracking Platform for SMI} $|$ \emph{React Native, Node.js, Postgres}}{2025}
          \resumeItemListStart
            \resumeItem{Developing full-stack web application to track child development, coach inputs, and volunteer activities}
            \resumeItem{Implemented gamified elements, real-time analytics, and secure user roles}
            \resumeItem{Built features including dashboards, leaderboards, and role-based access for nationwide deployment}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Secure Chat Application} $|$ \emph{Python, RSA Encryption, React, CI/CD}}{2025}
          \resumeItemListStart
            \resumeItem{Developed a full-stack chat platform enabling real-time encrypted communication between two users.}
            \resumeItem{Implemented end-to-end RSA encryption (2048-bit) with dynamic key exchange over custom socket connections.}
            \resumeItem{Built a responsive React interface with real-time message updates; tested with up to 10 concurrent users.}
            \resumeItem{Deployed frontend on Vercel and backend on Render, using GitHub Actions for automated CI/CD workflows.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Personal Portfolio Website} $|$ \emph{React, Framer Motion, GitHub Actions - CI/CD}}{2025}
          \resumeItemListStart
            \resumeItem{Designed and deployed a fully responsive personal portfolio using React and Framer Motion for smooth animations and dynamic transitions.}
            \resumeItem{Showcased 3+ projects with detailed case studies, GitHub links, and live demos highlighting frontend, backend, and AI/ML work.}
            \resumeItem{Integrated GitHub Actions for automated deployment and continuous integration, ensuring quick and consistent updates on each push.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Certificate of Completion -- IISER Mohali}{IISER Mohali}
        {AI-based Cardiovascular Risk Prediction Project}{2024 -- 2025}
        \resumeItemListStart
          \resumeItem{Recognized contributions in model development and system integration for year-long ML project}
        \resumeItemListEnd
      \resumeSubheading
        {Core Java (JSE) Programming Course}{Pinnacle Tech Programs}
        {45 hours of intensive training}{2024}
        \resumeItemListStart
          \resumeItem{Comprehensive training in Java fundamentals and object-oriented programming}
        \resumeItemListEnd
      \resumeSubheading
        {Deep Learning - Layers of Learning}{RVTechlearn \& PNT Academy}
        {18 hours Industrial Training and Winter Internship}{2024}
        \resumeItemListStart
          \resumeItem{Hands-on experience with deep learning frameworks and neural network architectures}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
    \resumeSubHeadingListStart
      \resumeSubheading
        {WERK - An Online Job Portal}{International Journal of Research and Publication Reviews (IJRPR)}
        {Research Paper Publication}{2024}
        \resumeItemListStart
          \resumeItem{Published comprehensive research on online job portal development and implementation}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, PHP, HTML/CSS, SQL} \\
     \textbf{Frameworks \& Technologies}{: React, Node.js, Next.js, Laravel, Tailwind CSS} \\
     \textbf{Machine Learning}{: Random Forest, XGBoost, SHAP, TensorFlow, Scikit-learn} \\
     \textbf{Databases}{: MongoDB, MySQL, PostgreSQL} \\
     \textbf{Cloud \& Tools}{: AWS, Firebase, Git, Docker} \\
     \textbf{Computer Vision}{: YOLOv11, ByteTrack, OpenCV}
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
